Storing messages with multipartite neural cliques

### 2014-07-07 Articles/article.tex
...

@@

		less biologically plausible rule

		same algorithmic complexity

		$w = a$	is optimal
		\begin{algorithm}
		\caption{$a$-sum of sum \label{asumsum}}

		\begin{algorithmic}
		\Require{}
		\Statex
		\While{$s < I$}
		\Let{a}{b}
		\If {$i\ge maxval$}
   	 	\State $i\gets 0$
		\Else
    		\If {$i+k\leq maxval$}
        	\State $i\gets i+k$ \Comment{$\oplus$: bitwise exclusive-or}
    		\EndIf
		\EndIf
		\EndWhile
		\end{algorithmic}
		\end{algorithm}

@@

	\begin{align}
	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{agc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
	\end{align}

@@

		\includegraphics[scale=0.55]{Courbes/5portant_psi_c8l256e4}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks \label{comppsi}}
	\end{figure}

>>>>

		To fully exploit the local regularity of the code (constant weight of $a$), we make a small modification the classic retrieving rule	by keeping activated all neurons that achieve a score equal or greater than the score appearing in $a$-th position in the ordered array of scores.

@@

		Although it is a less biologically plausible rule, it has the same algorithmic complexity, since selecting the $a$-th element in an array of $n$ elements is $O(n)$ in complexity.

		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$)

		\begin{algorithm}
		\caption{$a$-sum of sum \label{asumsum}}

		\begin{algorithmic}[1]
		\Require{i}
		\Procedure{Euclid}{$a,b$}
		\Statex
		\While{$s < I$}
		\Let{a}{b}
		\If {$i\ge maxval$}
   	 	\State $i\gets 0$
		\Else
    		\If {$i+k\leq maxval$}
        	\State $i\gets i+k$ \Comment{$\oplus$: bitwise exclusive-or}
    		\EndIf
		\EndIf
		\EndWhile
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

%	\begin{align}
%	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{agc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
%	\end{align}

	\begin{align*}
	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{agc} = n)  P(n_{bc} < n)^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) P(n_{bc} < n)^{l-2} P(n_{abc} < n) \right ]^{c_e}
	\end{align*}

@@

		\includegraphics[scale=0.55]{Courbes/5portant_psi_c8l256e4}
		\caption{Comparison of efficiencies between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks \label{comppsi}}
	\end{figure}
